Incremental λ-Calculus in Cache-Transfer Style

### 2017-08-22 popl18/target-language.tex
Fix incorrect description of target language let-bindings.

\paragraph{Syntax}
The syntax of $\target$ is defined in
Figure~\ref{fig:target-definition-syntax}. Base terms of $\target$
follow again $\lambda$-lifted A'NF, like
$\source$, except that a $\bf let$-binding for a function
application~$\tf\,\tx$ now binds an extra \textit{cache
  identifier}~$\tcacheid\ty\tf\tx$ instead of
output~$\ty$. Cache identifiers have non-standard syntax: it can
be seen as a triple that refers to the value identifiers $\tf$, $\tx$
and $\ty$. Hence, an $\alpha$-renaming of one of these three
identifiers must refresh the cache identifier accordingly.
Result terms explicitly return cache $\tcache$ through
syntax $(\tx, \tcache)$.
% A similar alpha-renaming issue must be made about the formal
% cache argument of caching-derivatives. In the Coq development,
% the positional approach to binders makes the problem disappear.

>>>>

\paragraph{Syntax}
The syntax of $\target$ is defined in
Figure~\ref{fig:target-definition-syntax}. Base terms of $\target$
follow again $\lambda$-lifted A'NF, like
$\source$, except that a $\bf let$-binding for a function
application~$\tf\,\tx$ now binds an extra \textit{cache
  identifier}~$\tcacheid\ty\tf\tx$ besides
output~$\ty$. Cache identifiers have non-standard syntax: it can
be seen as a triple that refers to the value identifiers $\tf$, $\tx$
and $\ty$. Hence, an $\alpha$-renaming of one of these three
identifiers must refresh the cache identifier accordingly.
Result terms explicitly return cache $\tcache$ through
syntax $(\tx, \tcache)$.
% A similar alpha-renaming issue must be made about the formal
% cache argument of caching-derivatives. In the Coq development,
% the positional approach to binders makes the problem disappear.
